Automatic prostate cancer detection through \acs*{dce}-\acs*{mri} images: all you need is a good normalization

### 2016-08-09 01_introduction/introduction.tex
Finish the introduction

The latter group of approaches are rather mathematical than pharmacokinetic modelling.

>>>>

The latter group of approaches are rather mathematical than pharmacokinetic modelling~\citep{huisman2001accurate,gliozzi2011phenomenological}.
These methods offer the advantages to not require any knowledge about the \ac{mri} sequence nor any conversion from signal intensity to concentration.
However, the heuristic approach propose by \citeauthor{huisman2001accurate} requires an estimate regarding the noise standard deviation of the signal as well as manual tuning.

Nevertheless, all presented methods suffer from two major drawbacks:
(i) the inter-patient variability of the data lead to a variation of the parameters estimated and to poor classification performance while designing \ac{cad} systems, and
(ii) only few parameters are used to characterize the dynamic signal implying that some information are discarded.

In this work, we propose a fully automatic normalization method for \ac{dce}-\ac{mri} that reduce the inter-patient variability of the data.
Furthermore, we show that using the full normalized signal lead to the best classification performance.

The paper is organized as follows: Section~\ref{sec:methods} outlines our normalization strategy (Section~\ref{sec:norm}) as well as specificity regarding the state-of-the-art methods used for comparison (Section~\ref{sec:stateart}). The dataset, experiments, and results are reported in Section~\ref{sec:experiments} while discussed in Section~\ref{sec:discussions} followed by a concluding section.

### 2016-08-09 main.tex
Add quantitative methods
Finish the introduction

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{00_files_system/model3-num-names}

@@

% Add authors and the different addresses
\author[label1,label3]{Guillaume~Lema\^itre\corref{cor1}}
\ead{g.lemaitre58@gmail.com}
\author[label3]{Robert~Mart\'i}
%\ead{marly@eia.udg.edu}
\author[label3]{Jordi~Freixenet}
%\ead{jordif@eia.udg.edu}
\author[label5]{Anke Meyer-Baese}
%\ead{ameyerbaese@fsu.edu}
\author[label4]{Joan~C.~Vilanova}
%\ead{kvilanova@comg.cat}
\author[label2]{Paul~M.~Walker}
%\ead{pwalker@u-bourgogne.fr}
\author[label1,label6]{Fabrice~Meriaudeau}
%\ead{fabrice.meriaudeau@u-bourgogne.fr}
\address[label1]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, 12 rue de la Fonderie, 71200 Le Creusot, France}
\address[label2]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, Avenue Alain Savary, 21000 Dijon, France}
\address[label3]{\scriptsize ViCOROB, Universitat de Girona, Campus Montilivi, Edifici P4, 17071 Girona, Spain}
\address[label4]{\scriptsize Department of Magnetic Resonance, Cl\'inica Girona, Lorenzana 36, 17002 Girona, Spain}
\address[label5]{\scriptsize Department of Scientific Computing, 400 Dirac Science Library, Florida State University, Tallahassee, FL 32306, United States}
\address[label6]{\scriptsize CISIR, Electrical \& Electronic Engineering Department, Universiti Teknologi Petronas, 32610 Seri Iskandar, Perak, Malaysia}
\cortext[cor1]{Corresponding author.}

>>>>

%% Vancouver numbered
%\usepackage{00_files_system/numcompress}\bibliographystyle{00_files_system/model3-num-names}

@@

% Add authors and the different addresses
\author[label1,label3]{Guillaume~Lema\^itre\corref{cor1}}
\ead{g.lemaitre58@gmail.com}
\author[label3]{Robert~Mart\'i}
%\ead{marly@eia.udg.edu}
%\author[label3]{Jordi~Freixenet}
%\ead{jordif@eia.udg.edu}
%\author[label5]{Anke Meyer-Baese}
%\ead{ameyerbaese@fsu.edu}
%\author[label4]{Joan~C.~Vilanova}
%\ead{kvilanova@comg.cat}
%\author[label2]{Paul~M.~Walker}
%\ead{pwalker@u-bourgogne.fr}
\author[label1,label6]{Fabrice~Meriaudeau}
%\ead{fabrice.meriaudeau@u-bourgogne.fr}
\address[label1]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, 12 rue de la Fonderie, 71200 Le Creusot, France}
%\address[label2]{\scriptsize LE2I UMR6306, CNRS, Arts et M\'etiers, Univ. Bourgogne Franche-Comt\'e, Avenue Alain Savary, 21000 Dijon, France}
\address[label3]{\scriptsize ViCOROB, Universitat de Girona, Campus Montilivi, Edifici P4, 17071 Girona, Spain}
%\address[label4]{\scriptsize Department of Magnetic Resonance, Cl\'inica Girona, Lorenzana 36, 17002 Girona, Spain}
%\address[label5]{\scriptsize Department of Scientific Computing, 400 Dirac Science Library, Florida State University, Tallahassee, FL 32306, United States}
\address[label6]{\scriptsize CISIR, Electrical \& Electronic Engineering Department, Universiti Teknologi Petronas, 32610 Seri Iskandar, Perak, Malaysia}
\cortext[cor1]{Corresponding author.}
